Experiment_2_modelling

### 2020-10-30 Experiment_2/Experiment_2_modelling.Rmd
draft3

##Self tuning EWA model

@@

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game), rps=A_RPS, fwg = A_FWG, shootout = A_SHOOT)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
      game_data <- subset(data, game == t_game)
      lik_hum[t] <- 1/nopts
      N <- 1.0

      R_t <- rep(0.0,nopts)
      H_t <- R_t

@@

      indx <- data[t,"round"]
      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])

      # Estimate phi(t)
      R_t <- as.numeric(names(Att) == a_act_prev)
      # cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
      # cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      # cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)

      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      for (i in 1:length(Att)) {
        action <- as.character(names(Att)[i])
        # cat("this is current strat",action,"\n")
        # cat("this is previous humna action",h_act_prev,"\n")

        # Attraction vector update rule 
        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
      }
      #Update the value of N 
      N <- Phi_t*N + 1
      #cat(Att,'\n')

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att)/sum(exp(lambda*Att))

      # Get actual human action and compute likelihood
      h_act <- as.character(game_data[indx,"h_action"])
      act_index <- match(h_act, names(Att))
      lik_hum[t] <- probs[[act_index]]
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

# exp2_EWA_self(1,test_data,"-2loglik")

@@

@@

for(id in unique(dat_exp2$human_id)) {
exp2_results <- rbind(exp2_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),
# 
# #                          # Bayesian updating with/without transfer
#                          "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
#                          "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
#                          "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
#                          "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),

                         #MS results for Bayesian models
                          # Bayesian updating with between and within game transfer
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 1*log(180),
                         "theta_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[1],

@@

                          # No distinction between players, transfer within and between
                         "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
                         "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
                         #

                         # # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         # "theta_transfer" = exp2_BT[[id]]$par[1],
                         # "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
                         # "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
                         # "theta_naive" = exp2_Naive[[id]]$par[1],
                         # # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         # "eps_transfer" = exp2_BT[[id]]$par[2],
                         # "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
                         # "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
                         # "eps_naive" = exp2_Naive[[id]]$par[2],

                         # Q-learning with last round states (No within transfer)
                         "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = exp2_QLS_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],

                         # QLS assuming within game transfer
                         "QLS_within_Tr_BIC" = exp2_QLS_within_Tr[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QLS_within_Tr_Beta" = exp2_QLS_within_Tr[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QLS_within_Tr_alpha" = exp2_QLS_within_Tr[[id]]$optim$bestmem[2],

                         # Self-Tuning EWA (only 1 parameter)
                          # BIC
                         "EWA_self_2LL" = exp2_SEWA_modelling[[id]]$optim$bestval,
                         "EWA_self_BIC" = exp2_SEWA_modelling[[id]]$optim$bestval + 1*log(180),
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "EWA_self_Lambda" = exp2_SEWA_modelling[[id]]$optim$bestmem[1],

                         # Model Based Model
                          # BIC
                         "MBM_2LL" = MBM2_modelling[[id]]$optim$bestval,
                         "MBM2_BIC" = MBM2_modelling[[id]]$optim$bestval + 2*log(180),
                          # Alpha is learning rate, beta is temperature in softmax
                         "MBM2_alpha" = MBM2_modelling[[id]]$optim$bestmem[1],
                         "MBM2_beta" = MBM2_modelling[[id]]$optim$bestmem[2]

@@

```{r}
# WIth IG results for Bayesian models
# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

# WIth MS results for Bayesian models
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
# WITH MS results for bayesian models 
# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
# 
#  write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
#  kable(exp2_table_results)
```

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)

  # IG BAYES MODELS 
  # min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
  # 
  # best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]

  # MS BAYES MODELS
  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]

  # 
  exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model_2" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         # "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "BT_minus_NBT_BIC" = id_results[,"Distinct_game_BIC"] - id_results[,"Distinct_stage_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

>>>>

##Self tuning EWA model (simple, no states)

@@

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    nopts <- 3
    # Resets at the beginning of each game and stage
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game), rps=A_RPS, fwg = A_FWG, shootout = A_SHOOT)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
      game_data <- subset(data, game == t_game)
      lik_hum[t] <- 1/nopts
      N <- 1.0

      # initialize H_t by looking at first action 
      a_act <- as.character(game_data[1,"a_action"])
      H_t <- as.numeric(colnames(Att) == a_act)

@@

      # rounds gets initialised at beginning of eahc stage so we can treat them as separate games and use
      # round as index 
      indx <- data[t,"round"]

      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])
      curr_state <- paste0(h_act_prev,a_act_prev)

      h_act <- as.character(game_data[indx,"h_action"])
      a_act <- as.character(game_data[indx,"a_action"])
      new_state <- paste0(h_act,a_act)

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))

      # Get actual human action and compute likelihood
      act_index <- match(h_act, colnames(Att))
      lik_hum[t] <- probs[[act_index]]

      # Update rule:
      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
      R_t <- as.numeric(colnames(Att) == a_act)
      #cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-1) + R_t)/(indx)
      #cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      #cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)
      delta_t <- as.numeric(reward[,a_act] >= as.numeric(game_data[indx,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
      state_indx <- match(curr_state,state_vec)
      Att[state_indx,] <- (Phi_t*N*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N + 1)

      ##############
      # for (i in 1:nopts) {
      #   action <- as.character(colnames(Att)[i])
      #   state_indx <- match(curr_state,state_vec)
      #   #cat("this is the current state index", state_indx, "\n")
      # 
      #   # Attraction vector update rule
      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
      # 
      # }
      # 
      #cat("this is the current Att vector", Att, "\n")
      ###################

      #Update the value of N 
      N <- Phi_t*N + 1

      #Update the state 
      curr_state <- new_state 
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}
```

@@

# Self-Tuning EWA model with states ( and possibly transfer)

exp2_STEWA_STATES <- function(par,data,return_value, transfer = TRUE){

  lambda <- par[1]
  nopts <- 3

  G3 <- expand.grid(c("left","center","right"), c("left","center","right"))    # Left, Center, Right 
  states_SHOOT <- paste0(G3$Var1,G3$Var2)

  A_RPS = matrix(-0.5,9,3)
  dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))

  A_FWG = matrix(-0.5,9,3)
  dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))

  A_SHOOT = matrix(-0.5,9,3)
  dimnames(A_SHOOT) = list(states_SHOOT, c("left","center","right"))

  # # Define reward matrices from the perspective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

   for(t in 1:nrow(data)) {
     # Get which game we are playing
     t_game <- data[t,"game"]

    if (data[t,"round"] == 1)  {

      # chance likelihood :we have no data on previous round.
      lik_hum[t] <- 1/nopts

      if (!transfer) {
        # switch and Reset attractions and reward matrices
        Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, shootout = A_SHOOT)
        state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, shootout = states_SHOOT)
        reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)

        # Get first ai action 
        a_act <- as.character(data[t,"a_action"])
        # initialize H_t by looking at first action
        H_t <- as.numeric(colnames(Att) == a_act)

        # Asumme N(0) = 1 for now...see discussion in paper
        N_t <- 1.0
        indx <- 1

      #Code for transfer , we're still in round 1 if loop  
      } else {

        if (data[t,"stage"] == 1) {

          # switch and Reset attractions and reward matrices
          Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, shootout = A_SHOOT)
          state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, shootout = states_SHOOT)
          reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
          # Get first ai action 
          a_act <- as.character(data[t,"a_action"])
          # initialize H_t by looking at first action
          H_t <- as.numeric(colnames(Att) == a_act)
          #initialize N_t and index
          N_t <- 1.0
          indx <- 1

        #round 1 stage 2
        } else if (data[t,"stage"] == 2) {
          Att_opp_1 <- Att
          H_opp_1 <- H_t
          N_opp_1 <- N_t
          indx  <- 1
          #reset Attractions
          Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, shootout = A_SHOOT)

        # round 1 stage 3  
        } else if (data[t,"stage"] == 3) {
          # we're in end of stage 2, so keep attractions and counts for stage 4
          Att_opp_2 <- Att
          H_opp_2 <- H_t
          N_opp_2 <- N_t
          indx <- 20
          # Get attractions and counts from stage 1
          Att <- Att_opp_1
          H_t <- H_opp_1
          N_t <- N_opp_1

        } else if (data[t,"stage"] == 4) {
          # get attractions and counts from end of stage 2
          Att <- Att_opp_2
          H_t <- H_opp_2
          N_t <- N_opp_2
          indx <- 20
        }
      }

      # Rounds 2 to end 
    } else {

      #cat("Attraction matrix", Att, "\n")

      # Get reward and past human action
      h_act_prev <- as.character(data[t-1,"h_action"])
      a_act_prev <- as.character(data[t-1,"a_action"])
      curr_state <- paste0(h_act_prev,a_act_prev)

      h_act <- as.character(data[t,"h_action"])
      a_act <- as.character(data[t,"a_action"])
      new_state <- paste0(h_act,a_act)

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))

      # Get actual human action and compute likelihood
      act_index <- match(h_act, colnames(Att))
      lik_hum[t] <- probs[[act_index]]

      # Update rule:
      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
      R_t <- as.numeric(colnames(Att) == a_act)
      #cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-1) + R_t)/(indx)
      #cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      #cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)
      delta_t <- as.numeric(reward[,a_act] >= as.numeric(data[t,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
      state_indx <- match(curr_state,state_vec)
      Att[state_indx,] <- (Phi_t*N_t*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N_t + 1)

      ##############
      # for (i in 1:nopts) {
      #   action <- as.character(colnames(Att)[i])
      #   state_indx <- match(curr_state,state_vec)
      #   #cat("this is the current state index", state_indx, "\n")
      # 
      #   # Attraction vector update rule
      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
      # 
      # }
      # 
      #cat("this is the current Att vector", Att, "\n")
      ###################

      #Update the value of N 
      N_t <- Phi_t*N_t + 1

      #Update the state 
      curr_state <- new_state

    }
   }  
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

```{r}
exp2_STEWA_STATES(1,test_data,"-2loglik", TRUE)

```
## Fitting ST_EWA_states WITHOUT transfer 
```{r, cache=TRUE}

exp2_STEWA_NT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_STEWA_NT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
#   exp2_STEWA_NT[[id]] <- optim(10.0,fn=exp2_STEWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  exp2_STEWA_NT[[id]] <- DEoptim(fn=exp2_STEWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", FALSE, control=list(trace = FALSE,parallelType=1))
}

save(exp2_STEWA_NT,file="exp2_STEWA_NT.RData")
```

## Fitting ST_EWA_states WITH transfer 
```{r, cache=TRUE}

exp2_STEWA_Tr <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_STEWA_Tr[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
#   exp2_STEWA_Tr[[id]] <- optim(10.0,fn=exp2_STEWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  exp2_STEWA_Tr[[id]] <- DEoptim(fn=exp2_STEWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", TRUE, control=list(trace = FALSE,parallelType=1))
}

save(exp2_STEWA_Tr,file="exp2_STEWA_Tr.RData")
```

@@

for(id in unique(dat_exp2$human_id)) {
exp2_results <- rbind(exp2_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),

                         ########## MS results for Bayesian models
                          # Bayesian updating with between and within game transfer
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 1*log(180),
                         "theta_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[1],

@@

                          # No distinction between players, transfer within and between
                         "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
                         "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
                          ###########

                         ########### Q-learning with last round states (No within transfer)
                         "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = exp2_QLS_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],
                         ############

                         ############# QLS assuming within game transfer
                         "QLS_within_Tr_BIC" = exp2_QLS_within_Tr[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QLS_within_Tr_Beta" = exp2_QLS_within_Tr[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QLS_within_Tr_alpha" = exp2_QLS_within_Tr[[id]]$optim$bestmem[2],
                         #############

                         ########## Self-Tuning EWA states NO transfer(only 1 parameter)
                          # BIC
                         "STEWA_NT_2LL" = exp2_STEWA_NT[[id]]$optim$bestval,
                         "STEWA_NT_BIC" = exp2_STEWA_NT[[id]]$optim$bestval + 1*log(180),
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "STEWA_NT_Lambda" = exp2_STEWA_NT[[id]]$optim$bestmem[1],
                         ###########

                          ########## Self-Tuning EWA states WITH transfer (only 1 parameter)
                          # BIC
                         "STEWA_Tr_2LL" = exp2_STEWA_Tr[[id]]$optim$bestval,
                         "STEWA_Tr_BIC" = exp2_STEWA_Tr[[id]]$optim$bestval + 1*log(180),
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "STEWA_Tr_Lambda" = exp2_STEWA_Tr[[id]]$optim$bestmem[1],
                         #############

                         ########### Model Based Model
                          # BIC
                         "MBM_2LL" = MBM2_modelling[[id]]$optim$bestval,
                         "MBM2_BIC" = MBM2_modelling[[id]]$optim$bestval + 2*log(180),
                          # Alpha is learning rate, beta is temperature in softmax
                         "MBM2_alpha" = MBM2_modelling[[id]]$optim$bestmem[1],
                         "MBM2_beta" = MBM2_modelling[[id]]$optim$bestmem[2]

@@

# WIth MS results for Bayesian models
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])

@@

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)

  # MS BAYES MODELS
  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)

  best_model <- c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]

  exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model_2" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         # "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "BT_minus_NBT_BIC" = id_results[,"Distinct_game_BIC"] - id_results[,"Distinct_stage_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
